appendix

### 2023-03-07 paper_comparison/appendix.Rmd
fill in basic demographic data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(visage)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(visage)
library(tidyverse)
```

@@

The education background of most participants have Diploma or Bachelor degrees, followed by High school or below. The survey data is gender balanced. Most of the participants are between 18 to 39.

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  ggplot() +
  geom_bar(aes(age_group, fill = pronoun), position = "dodge") +
  facet_wrap(~fct_relevel(education, "High School or below", "Diploma and Bachelor Degree", "Honours Degree", "Masters Degree")) +
  xlab("Age group") +
  ylab("Count")
```

Number of participants who have previous experience in experiment about reading data plots are not very different from the number of participants who haven’t. Age distributions are also similar for these two groups.

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  ggplot() +
  geom_bar(aes(age_group, fill = pronoun), position = "dodge") +
  facet_wrap(~previous_experience) +
  xlab("Age group") +
  ylab("Count")
```
